State of the Practice for Medical Imaging Software Based on Open Source Repositories

### 2024-11-15 StateOfPractice/Papers/SOP_MI_CritReviewsBioMedEng/SOP_MI_OSR.tex
Edits to Section 11 (Threats to Validity)

The measurement process used has previously been shown to be reasonably
reproducible, [citation redacted]
%% DOUBLE BLIND
%Smith et al.~\cite{SmithEtAl2016} 
reports grading five software products by two reviewers. Their rankings were
almost identical. As long as each grader uses consistent definitions, the
relative comparisons in the AHP results will be consistent between graders.

>>>>

The measurement process used has previously been shown to be reasonably
reproducible.
%% DOUBLE BLIND
%Smith et al.~\cite{SmithEtAl2016} 
[citation redacted] reports grading five software products by two reviewers.
Their rankings were almost identical. As long as each grader uses consistent
definitions, the relative comparisons in the AHP results will be consistent
between graders.
